RSV

### 2019-02-25 Analysis/RSV.Rmd
More useful overview plot

```{r setup, include=FALSE, error=FALSE, warning=FALSE, message=FALSE}
install.packages(c("dplyr", "zipcode", "reshape", "mgcv", "ggplot2", "gridExtra", "devtools", "data.table", "tikzDevice", "splitstackshape", "maps", "mapproj"))
library(devtools)
install_github("gavinsimpson/tsgam")
install_github("kassambara/easyGgplot2")
install_github("airbornemint/outbreak-predict")
```
```{r}
source("./RSV.R")
```

```{r}
ggplot(dataset %>% 
         group_by(weeki) %>%
         summarize(rsv=sum(rsv)), 
       aes(x=weeki, y=rsv)) +
  geom_hline(aes(yintercept = 0)) +
  geom_line() +
  labs(y="RSV cases/week", x="Time", title="All counties")

>>>>

```{r setup, include=FALSE, error=FALSE, warning=FALSE, message=FALSE}
install.packages(c("dplyr", "zipcode", "reshape", "mgcv", "ggplot2", "gridExtra", "devtools", "data.table", "tikzDevice", "splitstackshape", "maps", "mapproj", "rgdal", "rgeos", "scales"))
library(devtools)
install_github("gavinsimpson/tsgam")
install_github("kassambara/easyGgplot2")
install_github("airbornemint/outbreak-predict")
library(scales)
```
```{r}
source("./RSV.R")
```

```{r}
ggplot(datasetAll %>% 
         group_by(weeki, adate) %>%
         summarize(rsv=sum(rsv)), 
       aes(x=adate, y=rsv)) +
  geom_hline(aes(yintercept = 0)) +
  geom_line() +
  labs(y="RSV cases/week", x="Time", title="All counties") +
  scale_x_date(labels=date_format("%Y"), date_breaks="1 year")
